---
title: "Instructions to use canadacovidmetricsR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{canadacovidmetricsR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

## Usage

#### To use canadacovidmetricsR package in a project:

```{r setup}
library(canadacovidmetricsR)
```

This package is designed to provide key metrics regarding COVID-19 situation in Canada at province level using the data from [OpenCovid API](https://opencovid.ca/api/).

### Brief introduction:

The `canadacovidmetricsR` package helps obtain national or provincial level information on covid cases for a specific time period. There are 4 functions which will return key metrics, including total cumulative cases,
total cumulative deaths, total cumulative recovered cases and total
cumulative vaccine completion. This data is returned as an R Dataframe which can be used directly for further analysis, plotting or applying statistical models.

## Functions:

##### Obtain the total number of cases till date using get_cases():

-   `get_cases` Query total cumulative cases with ability to specify
    province and date range of returned data.
    
    Example usage:
    
    ``` r
     library(canadacovidmetricsR)
     
     get_cases(loc = "BC", date = "2020-01-31")
    ```
##### Obtain the total number of deaths till date using get_deaths():

-   `get_deaths` Query total cumulative deaths with ability to specify
    province and date range of returned data.
    
    Example usage:
    
    ``` r

     library(canadacovidmetricsR)
     
     get_deaths(loc = "BC", date = "2020-01-31")
    ```
##### Obtain the total number of recoveries till date using get_recoveries():

-   `get_recoveries` Query total cumulative recovered cases with ability
    to specify province and date range of returned data.
    
    Example usage:
    
    ``` r

    library(canadacovidmetricsR)
    
     get_recoveries(loc = "BC", date = "2020-01-31")
    ```
#### Obtain the total vaccinations using the get_vaccinations():

-   `get_vaccinations` Query total cumulative vaccine completion with
    ability to specify province and date range of returned data.
    
    Example usage:
    
    ``` r
     
     library(canadacovidmetricsR)
     
     get_vaccinations(loc = "BC", date = "2020-01-31")
    ```
    
## Key Advantages:

-   This package can be used to obtain granular data pertaining to a particular state or province as weel as national wide data.
-   Can be used by people without any need for coding expertise
-   There is scope for customization and the data obtained is easily readable.
  
    
    

    





















