---
title: "Instructions to use canadacovidmetricsR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{canadacovidmetricsR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

## Usage

#### To use Ranimalsgonewild package in a project:

```{r setup}
library(canadacovidmetricsR)
```

This package is designed to provide key metrics regarding COVID-19 situation in Canada at province level using the data from [OpenCovid API](https://opencovid.ca/api/).

The `canadacovidmetricsR` package helps 

## Functions:

Brief introduction:

-   `get_cases` Query total cumulative cases with ability to specify
    province and date range of returned data.

-   `get_deaths` Query total cumulative deaths with ability to specify
    province and date range of returned data.

-   `get_recoveries` Query total cumulative recovered cases with ability
    to specify province and date range of returned data.

-   `get_vaccinations` Query total cumulative vaccine completion with
    ability to specify province and date range of returned data.
    





















